Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-12 survey/survey.tex
added color to pic on p.13

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[densely dashed] (-1.6,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$ 
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[densely dashed] (-0.9,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\draw[densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
\end{center}
% \[ 
% ((t_1 * t_2) * t_3) * t_4 \leadsto
% (t_1 * t_2) * (t_3 * t_4) \leadsto
% t_1 * (t_2 * (t_3 * t_4))
% \]

@@

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[densely dashed] (-1.6,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$ 
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[densely dashed] (-1.25,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[densely dashed] (-1.5,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[densely dashed] (-1.25,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[densely dashed] (-1.0,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[densely dashed] (-0.9,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\draw[densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
\end{center}
% \[
% ((t_1 * t_2) * t_3) * t_4 \leadsto
% (t_1 * (t_2 * t_3)) * t_4 \leadsto
% t_1 * ((t_2 * t_3) * t_4) \leadsto
% t_1 * (t_2 * (t_3 * t_4))
% \]

>>>>

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.6,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$ 
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-0.9,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\draw[green,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
\end{center}
% \[ 
% ((t_1 * t_2) * t_3) * t_4 \leadsto
% (t_1 * t_2) * (t_3 * t_4) \leadsto
% t_1 * (t_2 * (t_3 * t_4))
% \]

@@

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.6,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$ 
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.25,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.5,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[red,densely dashed] (-1.25,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\draw[green,densely dashed] (-1.0,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\end{tikzpicture}
$\leadsto$
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.8}]
\node[above] (A) at (-2,0) {$t_1$}; 
\node[above] (B) at (-1.5,0) {$t_2$}; 
\node[above] (C) at (-1,0) {$t_3$}; 
\node[above] (D) at (-0.5,0) {$t_4$}; 
\draw[thick] (A) -- (-2,-1.5); 
\draw[thick] (B) -- (-1.5,-1.5); 
\draw[thick] (C) -- (-1,-1.5);; 
\draw[thick] (D) -- (-0.5,-1.5); 
\draw[green,densely dashed] (-0.9,-0.75) ellipse [x radius=0.85cm, y radius = 0.2cm];
\draw[red,densely dashed] (-0.75,-0.75) ellipse [x radius=0.4cm, y radius = 0.1cm];
\end{tikzpicture}
\end{center}
% \[
% ((t_1 * t_2) * t_3) * t_4 \leadsto
% (t_1 * (t_2 * t_3)) * t_4 \leadsto
% t_1 * ((t_2 * t_3) * t_4) \leadsto
% t_1 * (t_2 * (t_3 * t_4))
% \]
